Transient Variability In Vapor Intrusion And The Factors That Influence It

### 2018-10-12 tex/main.tex
Added new figures

% additional packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{array,multirow,graphicx}
\usepackage{comment}
\graphicspath{{./../figures/},{./../figures/air-exchange-rate/},{./../figures/kde-iacc-pressure/}}
\usepackage{lineno}
\linenumbers
% macros

@@

    \includegraphics[height=0.4\textheight,keepaspectratio]{asu-nas.pdf}

@@

\subsubsection{The Role Of Air Exchange Rate}
% Air exchange rate plots
\begin{figure}[htb!]
  \caption{Comparison between the recorded  and the calculated TCE in indoor air at the ASU house, assuming constant air exchange rate. \ref{fig:asu-iacc-ae-overview} shows the TCE in indoor air across time as well as the exchange rate. \ref{fig:violin-iacc-aet} shows the distribution of these values for three periods.}
  \label{fig:ae-analysis}
  % "Overview" plot
  \begin{subfigure}{\textwidth}
    \caption{ }
    \label{fig:asu-iacc-ae-overview}
    \includegraphics[width=\textwidth]{asu-iacc-ae-overview.png}
  \end{subfigure}
  % Violinplot figure
  \begin{subfigure}{0.75\textwidth}
    \caption{ }
    \label{fig:violin-iacc-aet}
    \includegraphics[width=\textwidth]{violin-asu-iacc.png}
  \end{subfigure}
\end{figure}\
Air exchange rate, which measures how often the interior air in a given building is exchanged with exterior air, is the main parameter characterizing contaminant expulsion, and another highly dynamic process.
Exploring the impact of fluctuations in air exchange rate is thus also important for the development of sampling strategies.
At the ASU house, the contaminant entry rate into the structure (called emission rate in that study) as well as the building air exchange rate were recorded across time.
This allows for exploration of the impact that fluctuating air exchange rate has on the final IACC by solving the CST equation, using the recorded contaminant entry rate as one input, and assuming a constant air exchange rate.
The rationale is to show the extent of variability in IACC due to factors other than fluctuations in air exchange rates.
We have taken this factor out of consideration by assuming a single constant exchange rate, characteristic of the whole period.

@@

@@

>>>>

% additional packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{array,multirow,graphicx}
\usepackage{comment}
\graphicspath{
  {./../figures/},
  {./../figures/air-exchange-rate/},
  {./../figures/kde-iacc-pressure/},
  {./../figures/preferential-pathway-sensitivity/},
  {./../figures/transient-response/}
}
\usepackage{lineno}
\linenumbers
% macros

@@

    \includegraphics[height=0.4\textheight,keepaspectratio]{nas-asu-house-iacc-deviating.pdf}

@@

\subsubsection{The Role Of Air Exchange Rate}
% Air exchange rate plots
\begin{figure}[htb!]
  \caption{Comparison between the recorded  and the calculated TCE in indoor air at the ASU house, assuming constant air exchange rate. \ref{fig:asu-iacc-ae-overview} shows the TCE in indoor air across time as well as the exchange rate. \ref{fig:violin-iacc-aet} shows the distribution of these values for three periods.}
  \label{fig:ae-analysis}
  % "Overview" plot
  \begin{subfigure}{\textwidth}
    \caption{ }
    \label{fig:asu-iacc-ae-overview}
    \includegraphics[width=\textwidth]{asu-iacc-ae-overview.png}
  \end{subfigure}
  % Violinplot figure
  \begin{subfigure}{0.75\textwidth}
    \caption{ }
    \label{fig:violin-iacc-aet}
    \includegraphics[width=\textwidth]{violin-asu-iacc.png}
  \end{subfigure}
\end{figure}
Air exchange rate, which measures how often the interior air in a given building is exchanged with exterior air, is the main parameter characterizing contaminant expulsion, and another highly dynamic process.
Exploring the impact of fluctuations in air exchange rate is thus also important for the development of sampling strategies.
At the ASU house, the contaminant entry rate into the structure (called emission rate in that study) as well as the building air exchange rate were recorded across time.
This allows for exploration of the impact that fluctuating air exchange rate has on the final IACC by solving the CST equation, using the recorded contaminant entry rate as one input, and assuming a constant air exchange rate.
The rationale is to show the extent of variability in IACC due to factors other than fluctuations in air exchange rates.
We have taken this factor out of consideration by assuming a single constant exchange rate, characteristic of the whole period.

@@

\begin{figure}[htb!]
  \caption{Sensitivity analysis of IACC dependence on indoor/outdoor pressure difference for a model featuring a PP (\ref{fig:ss-sensitivity-analysis-pp}) and without a PP (\ref{fig:ss-sensitivity-analysis-no-pp}). Results compared with field data from ASU house.}
  \label{fig:ss-sensitivity-analysis}
  % "Overview" plot
  \begin{subfigure}{0.55\textwidth}
    \caption{PP present. Sensitivity to the presence of a gravel sub-base and contamination in the PP considered.}
    \label{fig:ss-sensitivity-analysis-pp}
    \includegraphics[width=\textwidth]{yes-pp.pdf}
  \end{subfigure}
  % Violinplot figure
  \begin{subfigure}{0.55\textwidth}
    \caption{No PP preseent. Sensitivitiy to the presence of a gravel sub-base considered.}
    \label{fig:ss-sensitivity-analysis-no-pp}
    \includegraphics[width=\textwidth]{no-pp.pdf}
  \end{subfigure}
\end{figure}

@@

\end{comment}
